### 2020-09-14 paper/experiments.tex
Plots

\begin{figure}
  % \begin{subfigure}{.5\textwidth}
  %   \centering
  %   \input{plots/color.perf.t.in.out.csv.lines.pgf}
  %   \caption{Random perfect graphs}
  % \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.biparite18to48.t.in.out.csv.lines.pgf}
    \caption{Random bipartite graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.perfLin.t.in.out.csv.lines.pgf}
    \caption{Line graphs of random bipartite graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.grid5by4to9.t.in.out.csv.lines.pgf}
    \caption{Lattice graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.rookGraph6by4to8.t.in.out.csv.lines.pgf}
    \caption{Rook graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.knightGraph6by4to8.t.in.out.csv.lines.pgf}
    \caption{Knight graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering%
    \input{plots/color.hypercube20to40.t.in.out.csv.lines.pgf}
    \caption{Hypercube graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.split.t.in.out.csv.lines.pgf}
    \caption{Split graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.fullBinary20to45.t.in.out.csv.lines.pgf}
    \caption{Full binary trees}
  \end{subfigure}
  \caption{Overall times of CSDP Color}
\end{figure}

>>>>

\begin{figure}
  % \begin{subfigure}{.5\textwidth}
  %   \centering
  %   \input{plots/color.perf.t.in.out.csv.lines.pgf}
  %   \caption{Random perfect graphs}
  % \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.biparite18to48.t.in.out.csv.lines.pgf}
    \caption{Random bipartite graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.perfLin.t.in.out.csv.lines.pgf}
    \caption{Line graphs of random bipartite graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.lattice.t.in.out.csv.lines.pgf}
    \caption{Lattice graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.rook.t.in.out.csv.lines.pgf}
    \caption{Rook graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.knight.t.in.out.csv.lines.pgf}
    \caption{Knight graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering%
    \input{plots/color.hypercube.t.in.out.csv.lines.pgf}
    \caption{Hypercube graphs}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.split.t.in.out.csv.lines.pgf}
    \caption{Split graphs}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \input{plots/color.fullBinary.t.in.out.csv.lines.pgf}
    \caption{Full binary trees}
  \end{subfigure}
  \caption{Overall times of CSDP Color}
\end{figure}
